Hierarchical storage management in user space for neuroimaging applications

### 2025-07-19 paper/sea-neuro/paper-neuro.tex
Add paper updates and remove unused classes

\documentclass[fleqn,10pt]{wlscirep}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lineno}
\usepackage[binary-units]{siunitx}
\usepackage{multirow}
\usepackage{graphicx}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{xspace}
\usepackage{todonotes}

\newcommand{\TG}[1]{\todo[color=green!60!black]{\textbf{\textsc{From Tristan:}} #1\xspace}}

\linenumbers

\title{Hierarchical storage management in user space for neuroimaging applications}

\author{Val\'erie Hayot-Sasson}
\author{Tristan Glatard}
\affil{Department of Computer Science and Software Engineering, Concordia University, Montreal, Canada}

\begin{abstract}

  Neuroimaging open-data initiatives have led to increased availability of large
  scientific datasets. While these datasets are shifting the processing bottleneck
  from compute-intensive to data-intensive, current standardized analysis tools
  have yet to adopt strategies that mitigate the costs associated with large data
  transfers. A major challenge in adapting neuroimaging applications for data-intensive
  processing is that they must be entirely rewritten. To facilitate data management for
  standardized neuroimaging tools, we developed Sea, a library that intercepts and
  redirects application read and write calls to minimize data transfer time. In this
  paper, we investigate the performance of Sea on three preprocessing pipelines applied
  to three different neuroimaging datasets on two high-performance computing clusters.
  Our results demonstrate that Sea provides large speedups (up to 32$\times$) when the
  shared file system’s performance is deteriorated. When the shared file system is not
  overburdened by other users, performance is unaffected by Sea, suggesting that Sea’s
  overhead is minimal even in cases where its benefits are limited.

	% Neuroimaging open-data initiatives have led to increased availability of large
  % scientific datasets. While these datasets are shifting the processing
  % bottleneck from compute-intensive to data-intensive, current standardized
  % analysis tools have yet to adopt strategies that mitigate the costs
  % associated with large data transfers. A major challenge in adapting neuroimaging
  % applications for data-intensive processing is that they must be entirely
  % rewritten. To facilitate data management for standardized neuroimaging tools, we
  % developed Sea, a library that intercepts and redirects application read and
  % write calls to minimize data transfer time. In this paper, we investigate the
  % performance of Sea on three preprocessing pipelines implemented using standard toolboxes (FSL,
  % SPM and AFNI), using three neuroimaging datasets of different sizes
  % (OpenNeuro's ds001545, PREVENT-AD and the HCP dataset) on two high-performance
  % computing clusters. Our results demonstrate that Sea provides large speedups (up to 32$\times$) when
  % the shared file system's (e.g. Lustre) performance is deteriorated. When the
  % shared file system is not overburdened by other users, performance is
  % unaffected by Sea, suggesting that Sea's overhead is minimal even in cases
  % where its benefits are limited. Overall, Sea is beneficial, even when performance gain
  % is minimal, as it can be used to limit the number of files created on parallel file systems.
\end{abstract}
\begin{document}

\flushbottom
\maketitle
%  Click the title above to edit the author information and abstract

\thispagestyle{empty}

@@

@@

\begin{figure*}

    \centering
    \includegraphics[width=\columnwidth]{figures/sea-diagram.pdf}%
\caption{The Sea data-management library overview}
\label{fig:seaneuro:diagram}
\end{figure*}
    Sea (Figure~\ref{fig:seaneuro:diagram}) is a data-management library that leverages
    the \texttt{LD\_PRELOAD}
    trick to intercept POSIX file system calls, or more specifically, file access calls to the GNU C library,
    glibc, on Linux systems. This enables Sea to redirect write calls
    aimed at slower storage devices to a faster device whenever possible.
    Similarly, when intercepting read calls, Sea can choose to read from a
    faster device if a copy is available on that device. Sea decides which
    storage location it can write to based on the details provided in an
    initialization file called \texttt{sea.ini}. This file informs Sea of which
    locations it can use to read and write to, and well as their order of
    priority. Importantly, Sea is not a filesystem, but rather a
    lightweight tool that redirects files to more optimal storage devices.

@@

% \tristan{I find this section lacks a clear focus. What are the key points from
% these results? You should focus on them and possibly name your paragraphs
% accordingly, for improved clarity. My takeaways would be the following:
% \begin{enumerate} \item In controlled conditions, important speed-ups are
% observed. Mention min, average and max speed-up for all conditions. \item
% Speed-up is correlated with baseline makespan \item Other determinants of
% speed-up are unclear \item Overhead is minor \item Speed-ups are also observed
% in production cluster \end{enumerate}
% }
\begin{figure*}

\begin{subfigure}{0.5\textwidth}
    \centering
    \captionsetup{width=.85\linewidth}
    \includegraphics[width=\columnwidth]{figures/slashbin_nozoom.pdf}%
    \caption{Complete results}\label{fig:seaneuro:slashbinfull}
\end{subfigure}
\begin{subfigure}{0.5\textwidth}
    \centering
    \captionsetup{width=.85\linewidth}
    \includegraphics[width=\linewidth]{figures/slashbin_withzoom.pdf}
    \caption{Zoomed between 0 and 5000 seconds}\label{fig:seaneuro:slashbinzoom}
\end{subfigure}
\caption{Makespan comparison between Sea and Baseline on controlled dedicated cluster. Makespan
denotes the total time between execution launch and completion of the last computing task.}
\label{fig:seaneuro:slashbin}
\end{figure*}

@@

\begin{figure*}
\centering
\includegraphics[width=0.7\columnwidth]{figures/beluga_sea_tmpfs.pdf}%
\caption{Makespan comparison between Sea and tmpfs on the production cluster with flushing disabled}
\label{fig:seaneuro:tmpfs}
\end{figure*}

@@

\begin{figure*}

\begin{subfigure}{0.5\textwidth}
    \centering
    \captionsetup{width=.85\linewidth}
    \includegraphics[width=\columnwidth]{figures/beluga_withoutflush_nozoom.pdf}%
    \caption{Complete results}\label{fig:seaneuro:belugafull}
\end{subfigure}
\begin{subfigure}{0.5\textwidth}
    \centering
    \captionsetup{width=.85\linewidth}
    \includegraphics[width=\linewidth]{figures/beluga_withoutflush_zoom.pdf}
    \caption{Zoomed between 0 and 2000 seconds}\label{fig:seaneuro:belugazoom}
\end{subfigure}
\caption{Makespan comparison between Sea and Baseline on the production cluster with flushing disabled}
\label{fig:seaneuro:beluga-noflush}
\end{figure*}

\begin{figure*}
\begin{subfigure}{0.5\textwidth}
    \centering
    \captionsetup{width=.85\linewidth}
    \includegraphics[width=\columnwidth]{figures/beluga_withflush_nozoom.pdf}%
    \caption{Complete results}\label{fig:seaneuro:belugafullwf}
\end{subfigure}
\begin{subfigure}{0.5\textwidth}
    \centering
    \captionsetup{width=.85\linewidth}
    \includegraphics[width=\linewidth]{figures/beluga_withflush_zoom.pdf}
    \caption{Zoomed between 0 and 2000 seconds}\label{fig:seaneuro:belugazoomwf}
\end{subfigure}
\caption{Makespan comparison between Sea and Baseline on the production cluster with flushing enabled for all files}
\label{fig:seaneuro:beluga-wflush}
\end{figure*}

@@

    \subsection{Conclusion and Future work}

@@

    %Flushing - rely on modification time
    \section{Materials and Methods}

    \begin{table*}[t]
      \small\centering
    \resizebox{\textwidth}{!}{\begin{tabular}{|c c c c c|}
      \hline
      Dataset & Total Size (MB) & Total Number of images & Number of images per experiment & Total compressed size processed (MB) \\
      \hline
      \multirow{3}{*}{PREVENT-AD} & \multirow{3}{*}{289,532} &
      \multirow{3}{*}{53,061} & 1 & 52\\
      & & & 8 & 402\\
      & & & 16 & 732\\
      \hline
      \multirow{3}{*}{ds001545} & \multirow{3}{*}{27,377} &
      \multirow{3}{*}{1,778} & 1 & 282\\
      & & & 8 & 2115\\
      & & & 16 & 4167\\
      \hline
      \multirow{3}{*}{HCP} & \multirow{3}{*}{83,140,079} &
      \multirow{3}{*}{15,716,060*} & 1 &  1301\\
      & & & 8 & 5998\\
      & & & 16 & 8328\\

    \begin{table*}[t]
      \small\centering
      \resizebox{\textwidth}{!}{\begin{tabular}{|c c c c c c|}
      \hline
      Tool & Dataset &  Output Size (MB) & Total glibc calls & Glibc Lustre calls
      & Compute time (s)* \\
      \hline
      \multirow{3}{1em}{AFNI} & PREVENT-AD & 540 & 272,342 & 4,118 & 103.25 \\
      & ds001545 & 3,063 & 281,660 & 4,340 & 280.30 \\
      & HCP & 18,720 & 305,555 & 5,137 & 816.16 \\
      \hline
      \multirow{3}{1em}{FSL Feat} & PREVENT-AD & 254 & 191,148 & 28,099 &
      1,338.29 \\
      & ds001545 & 551 & 192,404 & 28,371 & 2,145.96 \\
      & HCP & 1,608 & 192,445 & 28,997 & 6,596.46 \\
      \hline
      \multirow{3}{1em}{SPM} & PREVENT-AD & 331.0 & 42,329 & 18,257 &  483.67 \\
      & ds001545 & 744 & 54,481 & 27,770 & 446.53 \\
      & HCP & 2,083 & 62,234 & 33,477 & 715.43 \\

@@

    \section{Data Availability}

@@

    \section{Code Availability}

@@

    \section{Acknowledgements}
    Val\'erie Hayot-Sasson was funded by the Canadian Open
    Neuroscience Platform (CONP) Scholar Award. This work
    was also supported by the Canada Foundation for Innova-
    tion as well as the Canada Research Chairs program.

    \section{Author Contributions}
    VHS contributed to idea development, experimental and model design, implementation of experiments and
    evaluation. TG contributed to idea development, experimental design and implementation.

    \section{Competing Interests}
    The authors declare no competing interests.

    \bibliography{biblio}

>>>>

\documentclass[pdflatex,sn-mathphys-num]{sn-jnl}

\usepackage[nopatch=footnote]{microtype}
\usepackage{url}
\usepackage{lineno}
% \usepackage[onehalfspacing]{setspace}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lineno}
\usepackage[binary-units]{siunitx}
\usepackage{multirow}
\usepackage{graphicx}
% \usepackage{caption}
\usepackage{subcaption}
\usepackage{xspace}
% \usepackage{graphicx}
% \usepackage{siunitx}

\usepackage{amsmath,amssymb,amsfonts}%
\usepackage{amsthm}%
\usepackage{mathrsfs}%
\usepackage[title]{appendix}%
\usepackage{xcolor}%
\usepackage{textcomp}%
\usepackage{manyfoot}%
\usepackage{booktabs}%
\usepackage{algorithm}%
\usepackage{algorithmicx}%
\usepackage{algpseudocode}%
\usepackage{listings}%

% \usepackage{todonotes}
% \usepackage{float}
% \newcommand{\TG}[1]{\todo[color=green!60!black]{\textbf{\textsc{From Tristan:}} #1\xspace}}

% \linenumbers

\theoremstyle{thmstyleone}%
\newtheorem{theorem}{Theorem}%  meant for continuous numbers
%%\newtheorem{theorem}{Theorem}[section]% meant for sectionwise numbers
%% optional argument [theorem] produces theorem numbering sequence instead of independent numbers for Proposition
\newtheorem{proposition}[theorem]{Proposition}% 
%%\newtheorem{proposition}{Proposition}% to get separate numbers for theorem and proposition etc.

\theoremstyle{thmstyletwo}%
\newtheorem{example}{Example}%
\newtheorem{remark}{Remark}%

\theoremstyle{thmstylethree}%
\newtheorem{definition}{Definition}%

\raggedbottom

\begin{document}

\title[Hierarchical storage management in user space for neuroimaging applications]{Hierarchical storage management in user space for neuroimaging applications}

%%% Use the \authfn to add symbols for additional footnotes, if any. 1 is reserved for correspondence emails; then continuing with 2 etc for contributions.

\author[1]{\fnm{Val\'erie} \sur{Hayot-Sasson}}%\email{valerie.hayot-sasson@concordia.ca}

\author*[1]{\fnm{Tristan} \sur{Glatard}}\email{tristan.glatard@concordia.ca}

\affil[1]{\orgdiv{Department of Computer Science and Software Engineering}, \orgname{Concordia University}, \orgaddress{\city{Montr\'eal}, \state{Qu\'ebec}, \country{Canada}}}

% \author[1]{Val\'erie Hayot-Sasson}
% \author[1,\authfn{1}]{Tristan Glatard}

% \affil[1]{Department of Computer Science and Software Engineering, Concordia University, Montreal, Qu\'ebec, Canada}

%%% Author Notes
% \authnote{\authfn{1}tristan.glatard@concordia.ca}

% %%% Paper category
% \papercat{Paper}

% %%% "Short" author for running page header
% \runningauthor{Hayot-Sasson and Glatard}

% \begin{frontmatter}
    % \onecolumn
    % \firstpage{1}

  %\title[Sea]{Hierarchical storage management in user space for neuroimaging applications}

  % \author[\firstAuthorLast ]{\Authors} %This field will be automatically populated
  % \address{} %This field will be automatically populated
  % \correspondance{} 
  % \extraAuth{}

  \abstract{Neuroimaging open-data initiatives have led to increased availability of large
  scientific datasets. While these datasets are shifting the processing bottleneck
  from compute-intensive to data-intensive, current standardized analysis tools
  have yet to adopt strategies that mitigate the costs associated with large data
  transfers. A major challenge in adapting neuroimaging applications for data-intensive
  processing is that they must be entirely rewritten. To facilitate data management for
  standardized neuroimaging tools, we developed Sea, a library that intercepts and
  redirects application read and write calls to minimize data transfer time. In this
  paper, we investigate the performance of Sea on three preprocessing pipelines applied
  to three different neuroimaging datasets on two high-performance computing clusters.
  Our results demonstrate that Sea provides large speedups (up to 32$\times$) when the
  shared file system’s performance is deteriorated. When the shared file system is not
  overburdened by other users, performance is unaffected by Sea, suggesting that Sea’s
  overhead is minimal even in cases where its benefits are limited.}

	% Neuroimaging open-data initiatives have led to increased availability of large
  % scientific datasets. While these datasets are shifting the processing
  % bottleneck from compute-intensive to data-intensive, current standardized
  % analysis tools have yet to adopt strategies that mitigate the costs
  % associated with large data transfers. A major challenge in adapting neuroimaging
  % applications for data-intensive processing is that they must be entirely
  % rewritten. To facilitate data management for standardized neuroimaging tools, we
  % developed Sea, a library that intercepts and redirects application read and
  % write calls to minimize data transfer time. In this paper, we investigate the
  % performance of Sea on three preprocessing pipelines implemented using standard toolboxes (FSL,
  % SPM and AFNI), using three neuroimaging datasets of different sizes
  % (OpenNeuro's ds001545, PREVENT-AD and the HCP dataset) on two high-performance
  % computing clusters. Our results demonstrate that Sea provides large speedups (up to 32$\times$) when
  % the shared file system's (e.g. Lustre) performance is deteriorated. When the
  % shared file system is not overburdened by other users, performance is
  % unaffected by Sea, suggesting that Sea's overhead is minimal even in cases
  % where its benefits are limited. Overall, Sea is beneficial, even when performance gain
  % is minimal, as it can be used to limit the number of files created on parallel file systems.
\keywords{data management, neuroimaging, high-performance computing}

\maketitle
% \end{frontmatter}

% \flushbottom
% \maketitle
% %  Click the title above to edit the author information and abstract

% \thispagestyle{empty}

@@

    \section{Materials and Methods}

    \begin{table*}[t]
      %\small
      \centering
    \resizebox{\textwidth}{!}{\begin{tabular}{|c c c c c|}
      \hline
      Dataset & Total Size (MB) & Total Number of images & Number of images per experiment & Total compressed size processed (MB) \\
      \hline
      \multirow{3}{*}{PREVENT-AD} & \multirow{3}{*}{289,532} &
      \multirow{3}{*}{53,061} & 1 & 52\\
      & & & 8 & 402\\
      & & & 16 & 732\\
      \hline
      \multirow{3}{*}{ds001545} & \multirow{3}{*}{27,377} &
      \multirow{3}{*}{1,778} & 1 & 282\\
      & & & 8 & 2115\\
      & & & 16 & 4167\\
      \hline
      \multirow{3}{*}{HCP} & \multirow{3}{*}{83,140,079} &
      \multirow{3}{*}{15,716,060*} & 1 &  1301\\
      & & & 8 & 5998\\
      & & & 16 & 8328\\

    \begin{table*}[t]
      %\small
      \centering
      \resizebox{\textwidth}{!}{\begin{tabular}{|c c c c c c|}
      \hline
      Tool & Dataset &  Output Size (MB) & Total glibc calls & Glibc Lustre calls
      & Compute time (s)* \\
      \hline
      \multirow{3}{*}{AFNI} & PREVENT-AD & 540 & 272,342 & 4,118 & 103.25 \\
      & ds001545 & 3,063 & 281,660 & 4,340 & 280.30 \\
      & HCP & 18,720 & 305,555 & 5,137 & 816.16 \\
      \hline
      \multirow{3}{*}{FSL Feat} & PREVENT-AD & 254 & 191,148 & 28,099 &
      1,338.29 \\
      & ds001545 & 551 & 192,404 & 28,371 & 2,145.96 \\
      & HCP & 1,608 & 192,445 & 28,997 & 6,596.46 \\
      \hline
      \multirow{3}{*}{SPM} & PREVENT-AD & 331.0 & 42,329 & 18,257 &  483.67 \\
      & ds001545 & 744 & 54,481 & 27,770 & 446.53 \\
      & HCP & 2,083 & 62,234 & 33,477 & 715.43 \\

@@

\begin{figure*}[t]

    \centering
    \includegraphics[width=\linewidth]{figures/sea-diagram.pdf}%
    \captionsetup{justification=centering}
    \captionof{figure}{The Sea data-management library overview}
    \label{fig:seaneuro:diagram}
\end{figure*}

    Sea (Figure~\ref{fig:seaneuro:diagram}) is a data-management library that leverages
    the \texttt{LD\_PRELOAD}
    trick to intercept POSIX file system calls, or more specifically, file access calls to the GNU C library,
    glibc, on Linux systems. This enables Sea to redirect write calls
    aimed at slower storage devices to a faster device whenever possible.
    Similarly, when intercepting read calls, Sea can choose to read from a
    faster device if a copy is available on that device. Sea decides which
    storage location it can write to based on the details provided in an
    initialization file called \texttt{sea.ini}. This file informs Sea of which
    locations it can use to read and write to, and well as their order of
    priority. Importantly, Sea is not a filesystem, but rather a
    lightweight tool that redirects files to more optimal storage devices.

@@

% \tristan{I find this section lacks a clear focus. What are the key points from
% these results? You should focus on them and possibly name your paragraphs
% accordingly, for improved clarity. My takeaways would be the following:
% \begin{enumerate} \item In controlled conditions, important speed-ups are
% observed. Mention min, average and max speed-up for all conditions. \item
% Speed-up is correlated with baseline makespan \item Other determinants of
% speed-up are unclear \item Overhead is minor \item Speed-ups are also observed
% in production cluster \end{enumerate}
% }

% %\setcounter{figure}{2}
% %\setcounter{subfigure}{0}
% \begin{subfigure}
% %\setcounter{figure}{2}
% %\setcounter{subfigure}{0}
%     \centering
%     \begin{minipage}[b]{0.5\textwidth}
%       \centering
%         \includegraphics[width=\linewidth]{figures/slashbin_nozoom.pdf}
%         \captionsetup{justification=centering}
%         \captionof{subfigure}{Complete results}\label{fig:seaneuro:slashbinfull}
%     \end{minipage}%
%     \begin{minipage}[b]{0.5\textwidth}
%       \centering
%         \includegraphics[width=\linewidth]{figures/slashbin_withzoom.pdf}
%         \captionsetup{justification=centering}
%         \captionof{subfigure}{Zoomed between 0 and 5000 seconds}\label{fig:seaneuro:slashbinzoom}
%     \end{minipage}

% %\setcounter{figure}{2}
% \setcounter{subfigure}{-1}
%     \caption{Makespan comparison between Sea and Baseline on controlled dedicated cluster. Makespan
%     denotes the total time between execution launch and completion of the last computing task.}
%     \label{fig:seaneuro:slashbin}
% \end{subfigure}

\begin{figure*}[ht]
\centering

\begin{subfigure}{0.8\textwidth}
    \centering
    \captionsetup{width=\textwidth}
    \includegraphics[width=\textwidth]{figures/slashbin_nozoom.pdf}%
    \caption{Complete results}\label{fig:seaneuro:slashbinfull}
\end{subfigure}
\begin{subfigure}{0.8\textwidth}
    \centering
    \captionsetup{width=\textwidth}
    \includegraphics[width=\textwidth]{figures/slashbin_withzoom.pdf}
    \caption{Zoomed between 0 and 5000 seconds}\label{fig:seaneuro:slashbinzoom}
\end{subfigure}
\caption{Makespan comparison between Sea and Baseline on controlled dedicated cluster. Makespan
denotes the total time between execution launch and completion of the last computing task.}
\label{fig:seaneuro:slashbin}
\end{figure*}

@@

\begin{figure*}[t]
\centering
\includegraphics[width=0.8\textwidth]{figures/beluga_sea_tmpfs.pdf}%
\caption{Makespan comparison between Sea and tmpfs on the production cluster with flushing disabled}
\label{fig:seaneuro:tmpfs}
\end{figure*}

@@

% \begin{subfigure}
%   %\setcounter{figure}{2}
%   %\setcounter{subfigure}{0}
%       \centering
%       \begin{minipage}[b]{0.5\textwidth}
%         \centering
%           \includegraphics[width=\linewidth]{figures/beluga_withoutflush_nozoom.pdf}
%           \captionsetup{justification=centering}
%           \captionof{subfigure}{Complete results}\label{fig:seaneuro:belugafull}
%       \end{minipage}%
%       \begin{minipage}[b]{0.5\textwidth}
%         \centering
%           \includegraphics[width=\linewidth]{figures/beluga_withoutflush_zoom.pdf}
%           \captionsetup{justification=centering}
%           \captionof{subfigure}{Zoomed between 0 and 2000 seconds}\label{fig:seaneuro:belugazoom}
%       \end{minipage}

%   %\setcounter{figure}{2}
%   \setcounter{subfigure}{-1}
%       \caption{Makespan comparison between Sea and Baseline on the production cluster with flushing disabled}
%       \label{fig:seaneuro:beluga-noflush}
%   \end{subfigure}

\begin{figure*}[h!]
  \centering

\begin{subfigure}{0.8\textwidth}
    \centering
    \captionsetup{width=\linewidth}
    \includegraphics[width=\textwidth]{figures/beluga_withoutflush_nozoom.pdf}%
    \caption{Complete results}\label{fig:seaneuro:belugafull}
\end{subfigure}
\begin{subfigure}{0.8\textwidth}
    \centering
    \captionsetup{width=\linewidth}
    \includegraphics[width=\textwidth]{figures/beluga_withoutflush_zoom.pdf}
    \caption{Zoomed between 0 and 2000 seconds}\label{fig:seaneuro:belugazoom}
\end{subfigure}
\caption{Makespan comparison between Sea and Baseline on the production cluster with flushing disabled}
\label{fig:seaneuro:beluga-noflush}
\end{figure*}

% \begin{subfigure}
%   %\setcounter{figure}{2}
%   %\setcounter{subfigure}{0}
%       \centering
%       \begin{minipage}[b]{0.5\textwidth}
%         \centering
%           \includegraphics[width=\linewidth]{figures/beluga_withflush_nozoom.pdf}
%           \captionsetup{justification=centering}
%           \captionof{subfigure}{Complete results}\label{fig:seaneuro:belugafullwf}
%       \end{minipage}%
%       \begin{minipage}[b]{0.5\textwidth}
%         \centering
%           \includegraphics[width=\linewidth]{figures/beluga_withflush_zoom.pdf}
%           \captionsetup{justification=centering}
%           \captionof{subfigure}{Zoomed between 0 and 2000 seconds}\label{fig:seaneuro:belugazoomwf}
%       \end{minipage}

%   %\setcounter{figure}{2}
%   \setcounter{subfigure}{-1}
%       \caption{Makespan comparison between Sea and Baseline on the production cluster with flushing enabled for all files}
%       \label{fig:seaneuro:beluga-wflush}
%   \end{subfigure}

\begin{figure*}[ht]
  \centering
\begin{subfigure}{0.8\textwidth}
    \centering
    \captionsetup{width=\linewidth}
    \includegraphics[width=\columnwidth]{figures/beluga_withflush_nozoom.pdf}%
    \caption{Complete results}\label{fig:seaneuro:belugafullwf}
\end{subfigure}
\begin{subfigure}{0.8\textwidth}
    \centering
    \captionsetup{width=\textwidth}
    \includegraphics[width=\textwidth]{figures/beluga_withflush_zoom.pdf}
    \caption{Zoomed between 0 and 2000 seconds}\label{fig:seaneuro:belugazoomwf}
\end{subfigure}
\caption{Makespan comparison between Sea and Baseline on the production cluster with flushing enabled for all files}
\label{fig:seaneuro:beluga-wflush}
\end{figure*}

@@

    \section{Conclusion and Future work}

@@

    %Flushing - rely on modification time

@@

    \section*{Data Availability}

@@

    \section*{Code Availability}

@@

    \section*{Declarations}
    Val\'erie Hayot-Sasson was funded by the Canadian Open
    Neuroscience Platform (CONP) Scholar Award. This work
    was also supported by the Canada Foundation for Innovation as well as the Canada Research Chairs program.

    \section*{Author Contributions}
    VHS contributed to idea development, experimental and model design, implementation of experiments and
    evaluation. TG contributed to idea development, experimental design and implementation.

    \section*{Competing Interests}
    The authors declare no competing interests.

    % \bibliographystyle{Frontiers-Harvard}
    \bibliography{biblio}
